{memer}: an R interface to the MEME Suite

### 2020-06-10 manuscript.Rmd
edit

```{bash, eval=F}
# Shell command setting random seed to 100
dreme -s 100 input.fasta
```

```{r, eval=F}
# memer command setting random seed to 100
runDreme(input_sequences, control = "shuffle", s = 100)
```

### Discriminative analysis
```{r}
sequences_list <- list("Static" = "seq",
                       "Increasing" = "seq",
                       "Decreasing" = "seq")

>>>>

Example of commandline flag as function input:
```{bash, eval=F}
# Shell command setting random seed to 100
dreme -s 100 input.fasta
```

```{r, eval=F}
# memer command setting random seed to 100
# user explicitly states they want to shuffle input sequences as control
runDreme(input_sequences, control = "shuffle", s = 100)
```

### Discriminative analysis
Care taken to enable a simple interface to create complex discriminative analysis designs
```{r}
sequences_list <- list("Static" = "seq",
                       "Increasing" = "seq",
                       "Decreasing" = "seq")
